ms2

### 2017-09-25 ms2/ms2_display.Rmd
new graphs
cleaner ms2 display

We ask if mean consumption $\mu$ has any information beyond fraction nonzero $f_>$ for predicting resistance $R$. We might expect that the simple two-part model represented by the regressions $R \sim f_>$ doesn't capture the fact that taking two doses should have a greater effect than taking one, etc.

These plots show the coefficient $\beta_\mu$ from the regression $R^{(u)} = \beta_0 + \beta_{f_>} f_>^{(u)} + \beta_\mu \mu^{(u)} + \varepsilon^{(u)}$.

```{r hrr_multi}
results %>%
  filter(model=='multivariate_fnz_mup', unit_type=='hrr', term=='mup') %>%
  interval_plot() +
  ylab(expression(beta[mu['>']])) +
  ggtitle("Linear multivariate (f> and mu>), HRR")
```

At the state level, none of the $\beta_\mu$ coefficients are significantly different from zero (after multiple-hypothesis correction).

```{r state_multi}
results %>%
  filter(model=='multivariate_fnz_mean', unit_type=='state', term=='mean') %>%
  interval_plot() +
  ylab(expression(beta[mu])) +
  ggtitle("Linear multivariate (f> and mean), state")
```

>>>>

### Effect along extensive margin $\mu_>$

```{r hrr_linear_mup}
results %>%
  filter(model=='univariate_mup', unit_type=='hrr', term=='mup') %>%
  interval_plot() +
  ylab(expression(beta[nu])) +
  ggtitle("Linear univariate, HRR")
```

### Effect beyond $f_>$

We ask if mean consumption $\mu$ has any information beyond fraction nonzero $f_>$ for predicting resistance $R$. We might expect that the simple two-part model (i.e., consuming or not) represented by the regressions $R \sim f_>$ doesn't capture the fact that taking two doses should have a greater effect than taking one, etc.

These plots show the coefficient $\beta_\nu$ from the regression $R = \beta_0 + \beta_{f_>} f_> + \beta_\nu \nu + \varepsilon$.

```{r hrr_multi}
results %>%
  filter(model=='multivariate_fnz_mup', unit_type=='hrr', term=='mup') %>%
  interval_plot() +
  ylab(expression(beta[nu])) +
  ggtitle("Linear multivariate (f> and nu), HRR")
```

At the state level, none of the $\beta_\nu$ coefficients are significantly different from zero (after multiple-hypothesis correction).

```{r state_multi}
results %>%
  filter(model=='multivariate_fnz_mup', unit_type=='state', term=='mup') %>%
  interval_plot() +
  ylab(expression(beta[nu])) +
  ggtitle("Linear multivariate (f> and nu), state")
```
